---
title: "MarkdownReport"
author: "Massimiliano Frabetti"
date: "2024-01-09"
output: html_document
---

# My first markdow document
Here you can add some text if you want

In this case I attain a result:
```{r, eval=T}
2 + 3
```
In this case I do not:
```{r, eval=F}
2 + 3
```

Using proper packages:
ImageRy package has been built at Alma Mater for learning remote sensing
```{r, eval=F}
library(imageRy)
```
Let's import some data, starting with a list of data:
```{r, eval=T}
library(imageRy)
im.list()
```
Import the Matogrosso area image:
```{r, eval=T, warning=F}
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```
Making a new plot of mato1992 with NIR on top of the green component of the RGB space: 
```{r, eval=T}
im.plotRGB(mato1992, r=2, g=1, b=3)
```
Plotting several images all together: 
```{r, eval=T}
par(mfrow=c(2,2))
im.plotRGB(mato1992, r=2, g=1, b=3)
im.plotRGB(mato1992, r=2, g=2, b=3)
im.plotRGB(mato1992, r=3, g=2, b=1)
im.plotRGB(mato1992, r=1, g=3, b=1)
```
Calculating spectral indices:
```{r, eval=T}
dvi <- mato1992[[1]] - mato1992[[2]]
dvi
```
Calculating spectral indices:
```{r, eval=T}
library(terra)
library(viridis)
dvi <- mato1992[[1]] - mato1992[[2]]
viridisc <- colorRampPalette(viridis(7))(255)
plot(dvi, col=viridisc)
 ```
Calculating variability:
```{r, eval=T}
sd5 <- focal(mato1992[[1]], matrix(1/25,5,5), fun=sd)
plot(sd5, col=viridisc)
```



